Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-25 paper.tex

CBRAIN\footnote{\url{http://cbrain.mcgill.ca}}~\cite{SHER-14} is an
open-source, web-based collaborative platform addressing the
challenges of data-heavy, computation-intensive neuroimaging
research. It offers transparent web-based access to remote data
sources, distributed computing sites, and an array of processing and
visualization tools, within a secure environment. CBRAIN is deployed
at a wide range of computing sites, including nine national HPC
centers in Canada, one in Korea, one in Germany, and on numerous local
servers. By September 2015, CBRAIN has served over 370 users across 50
cities in 19 countries who produced several high-impact results in the
field of neurosciences.

@@

Architectures to integrate workflow engines in science gateways are
diagrammed in Figure~\ref{fig:architectures} using the graphical
notations shown in Figure~\ref{fig:notations}.

@@

Software interactions among these components are represented with plain black
arrows.  \emph{Abstract} interactions are specific types of
interactions that may be implemented using different components and
interactions. They are represented with dotted arrows and labeled with
\texttt{*}. An architecture that has an abstract interaction is an
abstract architecture that can be instantiated in various ways.

>>>>

CBRAIN\footnote{\url{http://cbrain.mcgill.ca}}~\cite{SHER-14} is an
open-source\footnote{\url{https://github.com/aces/cbrain}}, web-based collaborative platform addressing the
challenges of data-heavy, computation-intensive neuroimaging
research. It offers transparent web-based access to remote data
sources, distributed computing sites, and an array of processing and
visualization tools, within a secure environment. CBRAIN is deployed
at a wide range of computing sites, including a network of national HPC
centers in Canada, one in Korea, one in Germany, and on numerous local
servers. As February 2016, CBRAIN has served over 420 users across 50
cities in 22 countries and has a national computing allocation of 660 CPU years
per annum.

@@

Architectures to integrate workflow engines in science gateways are
diagrammed in Figure~\ref{fig:architectures} using the graphical
notations shown in Figure~\ref{fig:notations}.
\note{Marc-e}{A few things bother me a bit with the notation fig., making it harder to assimilate
1- The interactions are padded in the middle of other stuff (Administrator, Data)
2- The Software component example says "Science gateway", should it not be empty?
3- The red arrow to explain the use of red; it looks like a very specific type
of interactions instead of the desired "any interactions or components can be red meaning...",
especially with 'a' and 'd' which the reader does not know the meaning yet.
Maybe a little red arrow and square with "Red used when specific to workflow execution"?
I don't have a great solution...
Red has special meaning, maybe remove it from the other pics (workflow eng, tasks)
as it creates lots of visual interference when looking for red?
4- Order in text jumps all over the fig notations. Explanations are given for, in order:
Components, workflow engine, interactions, abstract interactions, red color, tasks, data (no Administrator?)...
Could re-ordering the fig fix this? A figure figure legend could go a long way too (are there some in this journal?)
}

@@

Software interactions among these components are represented with
labeled, plain black arrows.  \emph{Abstract} interactions are
specific types of interactions that may be implemented using different
components and interactions. They are represented with dotted arrows
and labeled with \texttt{*}. An architecture that has an abstract
interaction is an abstract architecture that can be instantiated in
various ways.
